Scale Space Edge Detection

### 2018-03-07 paper.tex
Add gradient magnitude table

%&pdflatex
\documentclass{article}
\usepackage[final]{nips_2017}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{morefloats}
\usepackage{float}
\usepackage{listings}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{commath}
\usepackage{graphicx}

@@

>>>>

%&pdflatex
\documentclass{article}
\usepackage[final]{nips_2017}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{tabu}
\usepackage{morefloats}
\usepackage{float}
\usepackage{listings}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{commath}
\usepackage{graphicx}

@@

\begin{table}[t]
  \caption{Gradient magnitude}
  \centering
  \tabulinesep=0.1em
  \begin{tabu}to \textwidth{cX[c,m]X[c,m]X[c,m]}
    \toprule
    & Lena & Mandrill & Peppers\\
    \midrule
    $t = 0.1$ & \includegraphics[height=11em]{{{Images/lena/lena_GL_0.1}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GL_0.1}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GL_0.1}}}\\
    $t = 1.7$ & \includegraphics[height=11em]{{{Images/lena/lena_GL_1.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GL_1.7}}} & \includegraphics[height=11em]{{{Images/peppers/peppers_GL_1.7}}}\\
    $t = 18.7$ & \includegraphics[height=11em]{{{Images/lena/lena_GL_18.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GL_18.7}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GL_18.7}}}\\
    $t = 93.6$ & \includegraphics[height=11em]{{{Images/lena/lena_GL_93.6}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GL_93.6}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GL_93.6}}}\\
    $t = 256.0$ & \includegraphics[height=11em]{{{Images/lena/lena_GL_256.0}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GL_256.0}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GL_256.0}}}\\
    \bottomrule
\end{tabu}
\end{table}
